Draft

### 2021-03-01 notes/draft.Rmd
add sampling when needed

![Évolution des proba p(m|s) par rapport à la taille de corpus des MeSH m](/home/mxdelmas/Documents/Thèse/building_database/FORUM/kg-explorer/data/plot_proba_vs_corpus_mesh.png)

>>>>

![Évolution des proba p(m|s) par rapport à la taille de corpus des MeSH m](/home/mxdelmas/Documents/Thèse/building_database/FORUM/kg-explorer/data/Fig/plot_proba_vs_corpus_mesh.png)
